### 2016-03-10 paper/stereo.tex
yasu

\noindent To make the comparison simple, we restrict our proposal
generation to be constant-label proposals, and limit to binary fusion
(i.e., without multi-way fusion). Graph-cuts is used in fusing a
constant-label proposal as the energy is submodular. QPBO is used in
fusing a different solution from another thread as the energy is
non-submodular.  Due to the lack of multi-way fusion, the swarm fusion
architecture for the stereo problem is represented by the middle
example at the bottom of Fig.~\ref{fig:model}.

>>>>

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SFWSS (SF without solution sharing), SFWMF (SF without
multi-way fusion), and the standard SF.
%
For SFWSS, we have chosen $\alpha=2$ ($\beta=0$). For SFWMF, each thread
iterates the step of ($\alpha=1, \beta=0$) or ($\alpha=0, \beta=1$) so
that it can take a solution proposal in one step and a neighboring
solution in the next. For the standard SF, we have used ($\alpha=1, \beta=1$).
%
%
%
%
To make the comparison simple, we restrict our proposal
generation to be constant-label proposals. Graph-cuts is used in fusing
a constant-label proposal as the energy is submodular. QPBO is used in
fusing a different solution from another thread as the energy is
non-submodular.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.
